Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-22 writing/DraftExposurePaper/DraftExposurePaper.Rmd
tornado exposure

>>>>

```{r}
tornado_exposure <- county_events(counties = my_fips,
                             start_year = 1988, end_year = 2011,
                             event_type = "tornado")
tornado_2000 <- tornado_exposure %>%
        slice(1:2000) %>%
        group_by(fips) %>%
        summarise(count = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), count = as.numeric(count))
tornado_2000$value <- cut(tornado_2000$count, c(0, 1, 3, 5, 7, 9, 11, 13, 15), 
                   labels = c("0-1", "2-3", "4-5", "6-7", "8-9", "10-11", "12-13", "14-15"), 
                   include.lowest = TRUE)
exposure_palette <- brewer.pal(8, name = "YlGnBu")
map_tornado_2000 <- CountyChoropleth$new(tornado_2000)
map_tornado_2000$set_zoom(eastern_states)
map_tornado_2000$ggplot_scale <- scale_fill_manual(name = "Hits per\nCounty",
                                                values = exposure_palette,
                                                na.value = "white")
map_tornado_2000$title <- "Hits for top 2,000 Storm-County Pairs\nfor Tornado Events"
b <- map_tornado_2000$render()
```
